### 2023-02-02 README.Rmd
added paletteer demo

>>>>

## Bonus: 2568 palettes from **paletteer**

The R package [**paletteer**](https://github.com/EmilHvitfeldt/paletteer) contains 2568 from 70 other R packages. These have been converted to data for **cols4all** [(script)](https://github.com/mtennekes/cols4all/blob/main/build/build_paletteer.R)

These can be loaded and analysed as follows:

```{r}
paletteer_data = readRDS(url("https://github.com/mtennekes/cols4all/releases/download/v0.6/paletteer.rds","rb"))
c4a_sysdata_import(paletteer_data)
```

Note that we use `c4a_sysdata_import` rather than `c4a_load` because we want to replace all the palette data to avoid overlap and conflicts with the palettes already included in **cols4all**.

![https://user-images.githubusercontent.com/2444081/216455415-de676d12-8e94-4917-8adc-8ca1e6ac4df7.png](https://user-images.githubusercontent.com/2444081/216455415-de676d12-8e94-4917-8adc-8ca1e6ac4df7.png)

Note that this dashboard is not particularly fast (so grab a coffee:-))
